An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-24 poly-embed-journal/poly-embed-journal.tex
Flip flop order ontwo results

@@

The result above focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.

>>>>

Our first main result, Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.

@@
